The Perfect Bathtub Experience

### 2016-02-01 article/nontech.tex

\documentclass[12pt]{article}

@@

	Now going back to your bathtub, suppose you start you come home from a long day at work, eager to bathe and unwind. You start to fill your bathtub with warm water from its single faucet, and

>>>>

\documentclass[10pt]{article}

@@

	Now going back to your bathtub, suppose you come home from a long day at work, eager to bathe and unwind. You start to fill your bathtub with warm water from its single faucet. Unfortunately, you do not have a fancy tub with secondary heating systems like circulating jets, so the only way to warm your bathtub is through the faucet. Then you step in to the bathtub to clean and relax. After some time later, you notice the water in the tub is cooler than what you would like. How do you fix this?

	Using the faucet, turn on the water to slightly warmer than you would prefer. Now sure water is great heat retainer, but how about water entering the tub? How can we maintain the specific temperature of the bathtub water? Water is a liquid, so it takes the shape of its container. When water enters the bathtub, it will spread uniformly throughout the bathtub floor and accumulate upon itself due to gravity pulling the water molecules downward. Any substance does not like to stay warm however. Warmer temperatures like to diffuse to lower temperatures to promote a uniform temperature throughout. As such, the water in the bathtub will lose heat to the air above it and the surface of the bathtub. Because the faucet is positioned at one end of the bathtub and your body takes up solid space pushing water to the fringes of the bathtub, it's impossible to have perfectly uniform water temperature in your bath. However, the solution to this problem is to maintain constant water flow in the bathtub, even at a low pressure - this way the warm water will continually cycle into your bathtub and out the drain when it reaches a certain height. The loss of heat to the surrounding environment is taken into account for by the slightly warmer water temperature from the faucet.

	For those of you whom like to include bubble bath in your bathtub, you're in luck: bubble bath aids water's heat retention abilities by providing more outlets for water to push its heat towards. In the short term, you will have less issues maintaining your warm bubble bath for a longer period of time. In the long term however, you will need to resort to trickling water into the bathtub to maintain heat just like if you were not using bubble bath at all.

	And there it is folks! The perfect bath secrets exposed.
